Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-02 Paper.tex
Copied and pasted a formula with tiny in math mode to l. 2088 to see if it will pick up in the Travis CI build.

The proof-of-concept series includes a development premine, making the state root hash some value $stateRoot$. Also \hyperlink{H s}{$time$} will be set to the initial timestamp of the genesis block. The latest documentation should be consulted for those values.

\section{Ethash} \label{app:ethash}
\subsection{Definitions}
We employ the following definitions:

%\begin{tabularx}{\textwidth}{lrX}
\begin{tabu}{X[,l]X[,r]X[,l]}
\toprule
Name & Value & Description \hypertarget{Jwordbytes}{}\\
\midrule
$J_{\mathrm{wordbytes}}$ & 4  & This is the bytes in a word.\hypertarget{Jdatasetinit}{}\\
$J_{\mathrm{datasetinit}}$ & $2^{30}$ & This is the bytes in the dataset at genesis. \hypertarget{Jdatasetgrowth}{}\\
$J_{\mathrm{datasetgrowth}}$ & $2^{23}$ & This is the dataset growth per epoch. \hypertarget{Jcacheinit}{}\\
$J_{\mathrm{cacheinit}}$ & $2^{24}$ & This is the bytes in the cache at genesis.\hypertarget{Jcachegrowth}{}\\
$J_{\mathrm{cachegrowth}}$ & $2^{17}$ & This is the cache growth per epoch.\hypertarget{Jepoch}{}\\
$J_{\mathrm{epoch}}$ & 30000 & This is the blocks per epoch.\hypertarget{Jmixbytes}{}\\
$J_{\mathrm{mixbytes}}$ & 128 & This is the mix length in bytes.\hypertarget{Jhashbytes}{}\\
$J_{\mathrm{hashbytes}}$ & 64 & This is the hash length in bytes.\hypertarget{Jparents}{}\\
$J_{\mathrm{parents}}$ & 256 & This is the number of parents of each dataset element.\hypertarget{Jcacherounds}{}\\
$J_{\mathrm{cacherounds}}$ & 3 & This is the number of rounds in cache production.\hypertarget{Jaccesses}{}\\
$J_{\mathrm{accesses}}$ & 64 & This is the number of accesses in a hashimoto loop.\\
\bottomrule
\end{tabu}
%\end{tabularx}

>>>>

The proof-of-concept series includes a development premine, making the state root hash some value $stateRoot$. Also \hyperlink{H s}{$time$} will be set to the initial timestamp of the genesis block. The latest documentation should be consulted for those values.$\mathtt{\tiny KEC}\big(\mathtt{\tiny RLP}\big( () \big)\big)$

\section{Ethash}\label{app:ethash}
\subsection{Definitions}
We employ the following definitions:

%\begin{tabularx}{\textwidth}{lrX}
\begin{tabu}{X[,l]X[,r]X[,l]}
\toprule
Name & Value & Description \hypertarget{Jwordbytes}{} \\
\midrule
$J_{\mathrm{wordbytes}}$ & 4  & This is the bytes in a word.\hypertarget{Jdatasetinit}{}\\
$J_{\mathrm{datasetinit}}$ & $2^{30}$ & This is the bytes in the dataset at genesis. \hypertarget{Jdatasetgrowth}{} \\
$J_{\mathrm{datasetgrowth}}$ & $2^{23}$ & This is the dataset growth per epoch. \hypertarget{Jcacheinit}{}\\
$J_{\mathrm{cacheinit}}$ & $2^{24}$ & This is the bytes in the cache at genesis.\hypertarget{Jcachegrowth}{}\\
$J_{\mathrm{cachegrowth}}$ & $2^{17}$ & This is the cache growth per epoch.\hypertarget{Jepoch}{}\\
$J_{\mathrm{epoch}}$ & 30000 & This is the blocks per epoch.\hypertarget{Jmixbytes}{}\\
$J_{\mathrm{mixbytes}}$ & 128 & This is the mix length in bytes.\hypertarget{Jhashbytes}{}\\
$J_{\mathrm{hashbytes}}$ & 64 & This is the hash length in bytes.\hypertarget{Jparents}{}\\
$J_{\mathrm{parents}}$ & 256 & This is the number of parents of each dataset element.\hypertarget{Jcacherounds}{}\\
$J_{\mathrm{cacherounds}}$ & 3 & This is the number of rounds in cache production.\hypertarget{Jaccesses}{}\\
$J_{\mathrm{accesses}}$ & 64 & This is the number of accesses in a hashimoto loop.\\
\bottomrule
\end{tabu}
%\end{tabularx}
